Methods for Polyphonic Music Transcription

### 2013-12-11 paper/paper.tex
Fleshed out more sections of the paper

\section{Methodologies}
There are currently two main approaches to polyphonic music transcription. The first approach learns a supervised learning model that uses frequency magnitudes to predict the presence of a note. The second approach uses unsupervised learning techniques to extract

\subsection{Audio data}

Our training data comes from a large database of piano MIDI files. MIDI is a standard for specifying...
%musical score
%While MIDI specifies the type of instrument, 
% MIDI instrument not specified in the file 
%a standard for specifying

@@

\subsection{Note onset detection}
This method proposes restricting the problem to determining note onsets. This is a simpler problem than detecting note durations because of the possibility for time-varying timbres in instruments. Most researchers in this field evaluate their music transcription methods on their note onset detection performance.

\subsection{Discriminative models}
% SVM, logistic regression
\subsection{SVM}

% one vs all
\citet{poliner2006discriminative}

% frequency partition

@@

\citet{nam2011classification} proposes ...
 training a restricted Boltzmann machine on the spectrogram features. The features computed by the RBM are used by an SVM

@@

\subsection{Bayesian nonparametric models}
One of the downsides of the NMF methods is that they require the number of notes (or sources) to be specified

\subsection{Smoothing}
The raw output of many transcription techniques is often noisey and contains many short, spurious notes. Additionally, otherwise correctly transcribed notes may contain small unwanted gaps. Obviously these detracts from the quality of the transcription. Smoothing can be used to improve the transcription by removing the small errors described above. Some smoothing techniques are as simple as moving average or median filters, others take advantage of prior knowledge of the temporal structure of music.

@@

\subsubsection{Probabilistic spectral smoothness}

\subsection{Recurrent neural network}

@@

The MIDI music used to evaluate these methods came from the Classical Piano MIDI Page at http://www.piano-midi.de/, a free, online database of piano MIDI files with a wide range of composers. This database, along with the MAPS database, are a popular choice for piano transcription researchers. Table \ref{table:songs} on page 7 gives a list of the composers and songs we used for testing and training.

The MIDI files represent the ground truth data. To generate training data, we synthesized wav files from the MIDI files using Timidity...

Synthesized with Timidity -> 16kHz

@@

There is no standard metric to evaluate the performance of a transcription method. However, many researchers use the following methods:

@@

\section{Conclusion}
% Which method is fastest

>>>>

\section{Methodologies}
There are currently two main approaches to polyphonic music transcription. The first approach learns a supervised learning model that uses frequency magnitudes to predict the presence of a note. The second approach uses unsupervised learning techniques to simultaneously extract notes and a musical score from a spectrogram. The following sections detail the most popular techniques within these general approaches.

%\subsection{Audio data}

%Our training data comes from a large database of piano MIDI files. MIDI is a standard for specifying...
%musical score
%While MIDI specifies the type of instrument, 
% MIDI instrument not specified in the file 
%a standard for specifying

@@

\subsection{Note onset detection}
This method proposes restricting the problem to determining note onsets. This is a simpler problem than detecting note durations because of the possibility for time-varying timbres in instruments. Many researchers in this field evaluate their music transcription methods on their note onset detection performance. In this paper, we chose to evaluate our methods over the entire duration of the notes; while this brings us closer to the original musical score, it also results in higher error measures.

\subsection{Discriminative models}
% SVM, logistic regression
Applying discriminative machine learning models to detect notes is a dominant approach in transcription research. A discriminative model can be learned for each note (for pianos, 88 classifiers) over the frequency magnitudes of the song's spectrogram. Each note classifier outputs whether the note is present or absent at each time step determined by the time step used in the spectrogram. Many researchers have chosen nonlinear or kernel-based methods due to the complexity of the input space.

\subsection{SVM}

\citet{poliner2006discriminative}

% use support vector machines to predict note presence or absence at 10ms time steps based on

% one vs all
% frequency partition

@@

To increase the previous system's robustness to noise, \citet{nam2011classification} proposed a preprocessing stage using a restricted Boltzmann machine on the spectrogram features. The RBM would be able to learn noise invariant features over the spectrogram and provide a new input to the SVM classifiers. The researchers found a modest improvement in performance as they increased noise levels in their input data.

@@

\subsection{Bayesian nonparametric models}
One of the downsides of the NMF methods is that they require the number of notes (or sources) to be specified in advance. In piano transcription, we know that there are a constant 88 keys, but it is very often the case that only a subset of all keys will be used in a given song. Choosing the number of sources to be 88 in this case often results in duplicate notes or parts of notes in the dictionary matrix. \citet{blei2010bayesian} offers a Bayesian nonparametric method for transcription, similar to topic modeling, that automatically determines the appropriate number of sources.

\subsection{Smoothing}
One downside of the previous methods is that each time step and each note is classified independently of every other note. The raw output of these techniques is often noisy and contains many short, spurious notes. Additionally, otherwise correctly transcribed notes may contain small unwanted gaps. These gaps detract from the quality of the transcription. Smoothing can be used to improve the transcription by removing the small errors described above. Some smoothing techniques are as simple as moving average or median filters, others take advantage of prior knowledge of the temporal structure of music.

@@

%\subsubsection{Probabilistic spectral smoothness}
%\subsection{Recurrent neural network}

@@

The MIDI music we used to evaluate these methods comes from the Classical Piano MIDI Page\footnote{http://www.piano-midi.de/}, a free, online database of piano MIDI files with a wide range of composers. This database, along with the MAPS database, are a popular choice for piano transcription researchers. Table \ref{table:songs} on page 7 gives a list of the composers and songs we used for testing and training.

The MIDI files represent the ground truth data and the training labels for our classifiers. To generate training features, we synthesized the MIDI files into WAV files using Timidity++\footnote{http://timidity.sourceforge.net/}. Since the highest fundamental frequency on a piano is 4186Hz, we chose a sampling rate of 16kHz to capture the majority of the overtone frequencies. Many researchers choose an 8kHz sampling rate to decrease the size of their input data.

@@

There is no standard metric to evaluate the performance of a transcription method. Researchers use a variety of error measures, described in the sections below.

@@

\section{Conclusion}

We achieved the best results with...

% Which method is fastest
